---
title: "p8105_hw1_hc3451"
author: "Huanyu Chen"
date: "2023-09-15"
output: github_document
---

# Problem 1

```{r}
library(moderndive)

# Analyze Dataset
head(early_january_weather)
names(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```

The variables in this dataset includes: year, month, day, etc. with the value of int; temp, dewp, humid, etc. with the value of dbl.
This dataset has 235 rows and 15 columns.
The mean temperature is 39.58.

```{r}
library(ggplot2)

# Draw & Save Scatterplot
scatter_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time (Hour)", y = "Temperature", color = "Humidity")
print(scatter_plot)
ggsave("scatterplot_temp_vs_time_hour.png", plot = scatter_plot)
```

# Problem 2
```{r}
library(tidyverse)

# Create Data Frame
random_sample <- rnorm(10)
greater_0 <- random_sample > 0
character_vector <- sample(letters, 10, replace = TRUE)
factor_vector <- factor(sample(c("L1", "L2", "L3"), 10, replace = TRUE))

data_frame <- data.frame(
  random_sample, greater_0, character_vector, factor_vector)
head(data_frame)

# Calculate Mean Value
mean(pull(data_frame, random_sample))
mean(pull(data_frame, greater_0))

numeric_character_vector <- as.numeric(pull(data_frame, character_vector))
mean(numeric_character_vector)
numeric_factor_vector <- as.numeric(pull(data_frame, factor_vector))
mean(numeric_factor_vector)

```

Mean works for numeric data types (such as random_sample), but not for non-numeric types (such as character_vector and factor_vector).
For non-numeric types variables, converting them to numeric for mean calculation is a possible solution but does not work every time.