---
title: "p8105_hw1_hc3451"
author: "Huanyu Chen"
date: "2023-09-20"
output: github_document
---

# Problem 1

```{r, include=FALSE}
library(moderndive)
library(ggplot2)
library(tidyverse)
```

```{r}
# Analyze Dataset
data("early_january_weather")
names(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```

**The variables in this dataset includes: year, month, day, etc. with the value of int; temp, dewp, humid, etc. with the value of dbl. This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather$temp)`.**

```{r}
head(early_january_weather)

# Draw & Save Scatterplot
scatter_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(x = "Time (Hour)", y = "Temperature", color = "Humidity")
scatter_plot
ggsave("scatterplot_temp_vs_time_hour.png", plot = scatter_plot)
```

**Both humidity and temperature fluctuate approximately the same way in one day: during the daytime, the temperature is high and the humidity is high, while in the evening, the temperature and humidity are generally low.**

# Problem 2

```{r}
# Create Data Frame
random_sample <- rnorm(10)
greater_0 <- random_sample > 0
character_vector <- sample(letters, 10, replace = TRUE)
factor_vector <- factor(sample(c("L1", "L2", "L3"), 10, replace = TRUE))

data_frame <- data.frame(
  random_sample, greater_0, character_vector, factor_vector)
head(data_frame)

# Calculate Mean Value
mean(pull(data_frame, random_sample))
mean(pull(data_frame, greater_0))
```

```{r, eval=FALSE}
numeric_greater_0 <- as.numeric(pull(data_frame, greater_0))
mean(numeric_greater_0)
numeric_character_vector <- as.numeric(pull(data_frame, character_vector))
mean(numeric_character_vector)
numeric_factor_vector <- as.numeric(pull(data_frame, factor_vector))
mean(numeric_factor_vector)
```

**Mean works for numeric data types (such as random_sample), but not for non-numeric types (such as character_vector and factor_vector). For non-numeric types variables, converting them to numeric for mean calculation is a possible solution but does not work every time.**
